DATA 621 Homework #1

### 2019-09-25 hw1/doc/HW1.Rmd
Update HW1.Rmd
Added RMSE annotations to OOS error graphs

```{r}
moneyball_test$kitchen_sink <- predict(kitchen_sink, moneyball_test)
moneyball_test <- moneyball_test %>%
  mutate(kitchen_sink_error = TARGET_WINS - kitchen_sink)
ggplot(moneyball_test, aes(kitchen_sink_error)) +
  geom_histogram(bins = 50)
summary(moneyball_test$kitchen_sink_error)
```

@@

```{r}
moneyball_test$step_back <- predict(step_back, moneyball_test)
moneyball_test <- moneyball_test %>%
  mutate(step_back_error = TARGET_WINS - step_back)
moneyball_test %>%
  filter(step_back >0) %>%
  filter(step_back<182) %>% 
  ggplot(., aes(step_back_error)) +
  geom_histogram(bins = 50) +
  labs(caption = "Outlier removed")

@@

```{r}
moneyball_test$simple <- predict(simple_fit, moneyball_test)
moneyball_test <- moneyball_test %>%
  mutate(simple_error = TARGET_WINS - simple)
ggplot(moneyball_test, aes(simple_error)) +
  geom_histogram(bins = 50)
summary(moneyball_test$simple_error)
```

### Regression Ensemble 
```{r}
moneyball_test <- moneyball_test %>% mutate(ensemble_score = (kitchen_sink + step_back + simple)/3)
moneyball_test <- moneyball_test %>%
  mutate(ensemble_error = TARGET_WINS - ensemble_score)
ggplot(moneyball_test, aes(ensemble_error)) +
  geom_histogram(bins = 50)
summary(moneyball_test$ensemble_error)

>>>>

```{r}
moneyball_test$kitchen_sink <- predict(kitchen_sink, moneyball_test)
moneyball_test <- moneyball_test %>%
  mutate(kitchen_sink_error = TARGET_WINS - kitchen_sink)
ggplot(moneyball_test, aes(kitchen_sink_error)) +
  geom_histogram(bins = 50) +
  annotate("text",x=0,y=10,
           label = paste("RMSE = ",
                         round(sqrt(mean(moneyball_test$kitchen_sink_error^2)),2)
                         ),
           color="white"
           )
summary(moneyball_test$kitchen_sink_error)
```

@@

```{r}
moneyball_test$step_back <- predict(step_back, moneyball_test)
moneyball_test <- moneyball_test %>%
  mutate(step_back_error = TARGET_WINS - step_back)
moneyball_test %>%
  filter(step_back >0) %>%
  filter(step_back<182) %>% 
  ggplot(., aes(step_back_error)) +
  geom_histogram(bins = 50) +
  annotate("text",x=0,y=10,
           label = paste("RMSE = ",
                         round(sqrt(mean(moneyball_test$step_back_error^2)),2)
                         ),
           color="white"
           )
  labs(caption = "Outlier removed")

@@

```{r}
moneyball_test$simple <- predict(simple_fit, moneyball_test)
moneyball_test <- moneyball_test %>%
  mutate(simple_error = TARGET_WINS - simple)
ggplot(moneyball_test, aes(simple_error)) +
  geom_histogram(bins = 50) +
  annotate("text",x=0,y=10,
           label = paste("RMSE = ",
                         round(sqrt(mean(moneyball_test$simple_error^2)),2)
                         ),
           color="white"
           )
summary(moneyball_test$simple_error)
```

### Regression Ensemble 
```{r}
moneyball_test <- moneyball_test %>% mutate(ensemble_score = (kitchen_sink + step_back + simple)/3)
moneyball_test <- moneyball_test %>%
  mutate(ensemble_error = TARGET_WINS - ensemble_score)
ggplot(moneyball_test, aes(ensemble_error)) +
  geom_histogram(bins = 50) +
  annotate("text",x=0,y=10,
           label = paste("RMSE = ",
                         round(sqrt(mean(moneyball_test$ensemble_error^2)),2)
                         ),
           color="white"
           )
summary(moneyball_test$ensemble_error)
